### 2011-07-07 doc/theses/vitasek/diplomka.tex
Thesis: in progress, alpha version of Preface.

@@

TODO why is this important

TODO link to the article mentioning how few XMLs have schemas

@@

\nomenclature{MIP}{Mixed Integer Problem}

@@

@@

@@

\begin{itemize}
	\item Input -> How long the search for optimum lasts
	\item Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Which GLPK -> *
	\item Do I beat FIDAX with random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}

>>>>

% TODO what style of quotation marks to use?

@@

TODO why is this important - XMLs are extensively used but lack schemas (link Vosta's Even ant can create...).
We already have tools to infer the structure (see jInfer), now we would like to go a bit further - to find some integrity constraints to impose on these schemas.
Integrity schemas can be keys (with ID attributes as a "sub-group"), FKs, functional dependencies (quote Sviro?), etc.
We will focus on the first kind - ID and IDREF attributes.

\section{Structure of the thesis}

The thesis will be structured as follows.

First, we will introduce a few notions required throughout the work, such as XML tree, ID attributes, ID sets and keys for XML.

Secondly, we will review approaches to ID attribute and XML keys search from previous articles on this topic.

This will lead us to the NP-complete problem of maximal independent set (IS)\nomenclature{IS}{Independent Set}, where we will inspect approaches for solving it.

We will discuss a closely related Mixed Integer Problem (MIP)\nomenclature{MIP}{Mixed Integer Problem} and prove their "equality".

Afterwards, we will show how to use an external MIP solver and various heuristics to tackle this problem.

An extension to jInfer for finding ID attributes using MIP solver and a combination of heuristics will be presented and experimentally evaluated in the closing chapters.

@@

TODO rigorously define MIP - optimization problem, some of the variables integral

@@

\nomenclature{CH}{Construction Heuristic} %TODO decide on how to format CH/IH

@@

\nomenclature{IH}{Improvement Heuristic}

@@

\begin{itemize}
  \item Which construction heuristic is the best - limit GLPK to like 1 second
  \item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
  \item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Which GLPK -> *
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}
